---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
library(siconfiBD)
library(readr)
projeto <- read_csv("projeto.csv")
set_billing_id(projeto$projeto) 

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# siconfiBD

<!-- badges: start -->
<!-- badges: end -->

The goal of siconfiBD is to get public financial data from Brazillian municipalities

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("tchiluanda/siconfiBD")
```
## Example

This is a basic example which shows you how to get government functions for municipalities of a given state vector:

```{r example}
library(siconfiBD)
## You need a Google Cloud Project and then set this project using the funcion below just before use the
## functions to retrieve data
#set_billing_id(<your_project_id>) 


exp_mun_state<- get_function_expenses_municipality_state(year=2019, state = "AP", gov_function = "Saúde", expense_stage= "Despesas Pagas")

head(exp_mun_state)
```

or maybe you want the data for some expense account of a given municipality.

```{r example2}
exp_mun<- get_budgetary_expenses_municipality(year = 2019,municipality = 3550308, account = "Pessoal e Encargos Sociais")

head(exp_mun)
```

if you are not sure what are the government functions available you can use something like this:

```{r example3}
gov_func<- get_distinct_function()

head(gov_func)

```

